Trip Summary ITHIM-R

### 2021-03-17 code/producing_trips_rd/trip-summary.Rmd
Simple changes in script
Adding some survey details

@@

  Missing = c("N/A", 

@@

                      "No, walking trips are only considered when it is a unique mode. It never appears combined with other modes",

@@

         "--", "--", "--", "--", "--", "--"),

@@

           "Need to check if injuries dataset covers the same area that time use survey does.")

>>>>

  year = c("2010",
           "2017",
           "2012",
           "2017",
           "2019",
           "2012",
           "",
           "",
           "",
           "",
           ""),
  # Definition of a trip
  Trip_definition = c(
    # BA: Pag 23- Report.pdf
    "Moving from a origin to a destiny with a specific reason/motive",
                      "Moving for a specific reason between two specific points (origin and destination), using one or more modes of transport. Walking trips where the reason for the trip is work or school, regardless of the distance travelled; or the distance covered is more than 500 mts for other reasons.",
    # Belo Horizonte: pag 16, "Codebook and protocol.pdf"
    "Moving from one part to another with a specific reason/motive, using one or more modes of transport",
                      "Moving from one part to another with a specific reason/motive, using one or multiples modes of transport",
                      "Moving from one part to another with a specific reason/motive, a definite hour of start and end, a mode of transport, and a duration greater than 3 minutes. Or moving from one part to another with reason/motive work or study of any duration",
                      "Any movement carried out on public roads with a purpose
determined, between two places (origin and destination) at a certain time of day; It can be carried out in several modes of transport and consist of one or more stages",
"",
"",
"",
"",
""),
  Reference_period = c(
    # BA: page 4, report.pdf
    "Trips made in working days",
    "Trips made the day before the survey (from 4am yesterday to 3:59am today).",
    "",
                       "Trips made during the week (Tuesday, Wednesday, Thursday) and in Saturdays (weekends)",
                       "Trips made the day of reference, i.e., the day before the survey (from 4am yesterday to 4am today). Surveys made from Monday to Sunday (according to the dataset).",
                       "Trips made in working days (regular season), in weekends (regular season) and in working days(summer season)",
                       "",
                       "",
                       "",
                       "",
                       ""),

@@

  Stage_missing = c("N/A", 

@@

@@

Walking_in_trip_duration = c("Not sure, yet.",
                             "",
                             "",
                             "",
                             "",
                             "",
                             "",
                             "",
                             "",
                             "",
                             ""),

@@

           "Need to check if injuries dataset covers the same area that time use survey does."),
         "--", "--", "--", "--", "--", "--")
